Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-14 docs/ms.tex
Update ms.tex

\subsection{Posterior Samples}

We show the posterior samples of both $g$ and $\vec{\alpha}$, for both beta
function and step function model.

The probability distribution can be visualised by plotting points at each sample
position. An example in the x, y plane is shown for the posterior distribution of
$g$ in 64 sky patches in Figure 1. There are 8 galaxies in each patch in the simulation.
The number density of samples is proportional to the probability density. The figure shows that the two parameters of $\vec{g}$
do not have strong correlation, since the shape of smaples is close to a circle.
We also shows the histogram of g1 in a single sky patch in Figure 2. Not surprisingly it is close to a Gaussian distribution.
If the probability distribution of parameters are perfect Gaussian, the most probable estimates and uncertainty 
is just the mean and standard deviation of the Gaussian distribution. However, in pratical, we find that the distribution 
of reduced shear $\vec{g}$ will  get closer to Gaussian, when larger number of galaxies in one patch  is used. When the number of galaxies in 
one patch is equal to or larger than 8, we found it's eligible to make such an approximation that to use sample mean and standard 
deviation as the most probable estimates and uncertainty. We'll justify this approximation with a bias test in the following
sub section.

>>>>

\subsection{Posterior Samples}
The probability distribution can be visualised by plotting points at each sample
position. An example in the x, y plane is shown for the posterior distribution of
$g$ in 64 sky patches in Figure 1. There are 8 galaxies in each patch in the simulation.
The number density of samples is proportional to the probability density. The figure shows that the two parameters of $\vec{g}$
do not have strong correlation, since the shape of smaples is close to a circle.
We also shows the histogram of g1 in a single sky patch in Figure 2. Not surprisingly it is close to a Gaussian distribution.
If the probability distribution of parameters are perfect Gaussian, the most probable estimates and uncertainty 
is just the mean and standard deviation of the Gaussian distribution. However, in pratical, we find that the distribution 
of reduced shear $\vec{g}$ will  get closer to Gaussian, when larger number of galaxies in one patch  is used. When the number of galaxies in 
one patch is equal to or larger than 8, we found it's eligible to make such an approximation that to use sample mean and standard 
deviation as the most probable estimates and uncertainty. We'll justify this approximation with a bias test in the following
sub section.
